Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-02-12 Paper.tex
9.4.3. Jump Destination Validity - treat code as reachable by PC

We previously used $D$ as the function to determine the set of valid jump destinations given the code that is being run. We define this as any position in the code occupied by a {\small JUMPDEST} instruction.

All such positions must be on valid instruction boundaries, rather than sitting in the data portion of {\small PUSH} operations and must appear within the explicitly defined portion of the code (rather than in the implicitly defined \hyperlink{stop}{{\small STOP}} operations that trail it).

Formally:
\begin{equation}
D(\mathbf{c}) \equiv D_{\mathrm{J}}(\mathbf{c}, 0)
\end{equation}

where:
\begin{equation}
D_{\mathrm{J}}(\mathbf{c}, i) \equiv \begin{cases}
\{\} & \text{if} \quad i \geqslant \lVert \mathbf{c} \rVert  \\
\{ i \} \cup D_{\mathrm{J}}(\mathbf{c}, N(i, \mathbf{c}[i])) & \\
\quad\quad\text{if} \quad \mathbf{c}[i] = \text{\small JUMPDEST} \\
D_{\mathrm{J}}(\mathbf{c}, N(i, \mathbf{c}[i])) & \text{otherwise} \\
\end{cases}
\end{equation}

where $N$ is the next valid instruction position in the code, skipping the data of a {\small PUSH} instruction, if any:
\begin{equation}
N(i, w) \equiv \begin{cases}
i + w - \text{\small PUSH1} + 2 & \\
\quad\quad\text{if} \quad w \in [\text{\small PUSH1}, \text{\small PUSH32}] \\
i + 1 & \text{otherwise} \end{cases}
\end{equation}

>>>>

We define this as any position in the code occupied by a {\small JUMPDEST} instruction.

All such positions must appear within the explicitly defined portion of the code (rather than in the implicitly defined \hyperlink{stop}{{\small STOP}} operations that trail it).
